% \skills{PhD in Physics}, \textit{Université Grenoble Alpes}, \href{https://theses.hal.science/tel-00493016/document}{\textit{High-Density Near-Field Optical Disc Recording}} (Doctoral dissertation) \hfill November 2004 - November 2007

% \skills{Engineer's Diploma}, \textit{Ecole Supérieure d'Optique - Institut d'Optique Graduate School} \hfill 2001 - 2004

% %\skills{Research Master Degree in Physics: matter-wave interactions}, \textit{Paris-Sud University (Paris XI)} \hfill 2003 - 2004
% \skills{Research Master Degree in Physics: matter-wave interactions}, \textit{Paris-Sud University (Paris XI)}, \href{https://www.researchgate.net/profile/C-Lepers/publication/237587056_AMELIORATION_DE_LA_SENSIBILITE_D%27UN_DISPOSITIF_OLCR_PAR_INTERPOLATION_RECADRAGE_ET_SOMMATION_D%27INTERFEROGRAMMES/links/00b7d53c53c4232e86000000/AMELIORATION-DE-LA-SENSIBILITE-DUN-DISPOSITIF-OLCR-PAR-INTERPOLATION-RECADRAGE-ET-SOMMATION-DINTERFEROGRAMMES.pdf}{\textit{Improving the sensitivity of an OLCR device by interpolation, recentering and summing interferograms}} \hfill 2003 - 2004

% \skills{Intensive two-year undergraduate course in Mathematics and Physics}, \textit{CPGE Joffre, PCSI, PC*} \hfill 1999 - 2001


\begin{multicols}{2}

\skills{PhD in Physics}, \textit{Université Grenoble Alpes}, \href{https://theses.hal.science/tel-00493016/document}{\textit{High-Density Near-Field Optical Disc Recording}} (Doctoral dissertation) \hfill November 2004 - November 2007
\begin{itemize}
\item Focused on breakthrough research in Near-Field High Density Optical Data Storage.
\item Designed innovative super-resolving optical heads for data storage, including new solid immersion lens and plasmonics components.
\item Demonstrated an experimental system capable of recording/reading 1.5 Terabytes on a single 12cm diameter optical disk, surpassing traditional resolution limits.
\item Filed five patents based on the new system architecture and experimental proof of concept.
\end{itemize}

\skills{Engineer's Diploma}, \textit{Ecole Supérieure d'Optique - Institut d’Optique Graduate School} \hfill 2001 - 2004
\begin{itemize}
\item Specialized in Optics and Photonics, with a focus on signal and image processing.
\item Gained comprehensive knowledge in advanced optics technologies and applications.
\end{itemize}

\skills{Research Master Degree in Physics: matter-wave interactions}, \textit{Paris-Sud University (Paris XI)}, \href{https://www.researchgate.net/profile/C-Lepers/publication/237587056_AMELIORATION_DE_LA_SENSIBILITE_D%27UN_DISPOSITIF_OLCR_PAR_INTERPOLATION_RECADRAGE_ET_SOMMATION_D%27INTERFEROGRAMMES/links/00b7d53c53c4232e86000000/AMELIORATION-DE-LA-SENSIBILITE-DUN-DISPOSITIF-OLCR-PAR-INTERPOLATION-RECADRAGE-ET-SOMMATION-DINTERFEROGRAMMES.pdf}{\textit{Improving the sensitivity of an OLCR device by interpolation, recentering and summing interferograms}} \hfill 2003 - 2004
\begin{itemize}
\item Conducted in-depth research on enhancing the sensitivity of Optical Low Coherence Reflectometry (OLCR) devices.
\item Developed and validated a new method for improving OLCR measurements.
\end{itemize}

\skills{Intensive two-year undergraduate course in Mathematics and Physics}, \textit{CPGE Joffre, PCSI, PC*} \hfill 1999 - 2001
\begin{itemize}
\item Completed a rigorous preparatory program in Mathematics and Physics, laying a solid foundation for advanced studies in Physics.
\end{itemize}


\end{multicols}